Regular singular Volterra equations on complex domains

### 2023-07-26 reg-sing-volterra.tex
Version of the proof where we take the expansion of p/q

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Main result}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\begin{thm}
Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R}, \]
where
\begin{itemize}
\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item a simple zero at $\zeta = 0$,
\item no zeros in $\Omega$ (as the next condition implies), and
\item a positive lower bound $C_p |z|^d \le |p|$;
\end{itemize}
\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item an upper bound $|q| \le C_q |z|^{d-1}$; and
\end{itemize}
\item $\mathcal{R}$ is an integral kernel operator
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
where $k$ is a holomorphic function on $\Omega^2$, with
\begin{itemize}
\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$.
\end{itemize}
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.

For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
\[ \mathcal{V}f = 0 \]
has a unique solution in the affine subspace
\[ \zeta^{\tau-1} + \holoL{\infty, \tau-1+\epsilon}_\Lambda(\Omega) \]
of the function space $\holoL{\infty, \tau-1}_\Lambda(\Omega)$, defined in Section~\ref{fn-spaces}.
\end{thm}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

@@

We now know that by setting $\Lambda > \lambda$ and then increasing $\Lambda$ as needed, we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. This completes our proof of Proposition~\ref{get-contraction}.
%%Let's again integrate along a straight path, where the fact that $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$ allows us to combine the exponential factors in our bound:
%%\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|. \]
%%This time, we'll use the parameterization $\zeta = s \frac{\zeta(a)}{|\zeta(a)|}$, with $s \in (0, |\zeta(a)|]$:
%%\begin{align*}
%%|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{|\zeta(a)|} \left(\frac{s}{|\zeta(a)|}\right)^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
%%\end{align*}
%------------------------------------------------------------------------
\color{SteelBlue}
\section{Integro-differential equations {[from {\tt airy-resurgence}]}}
\textcolor{DarkTurquoise}{\textbf{Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}}
\subsection{Existence of solutions}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
\begin{align*}
\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
\phi & \mapsto \zeta^{-\sigma} \phi
\end{align*}
is an isometry. More generally,
\begin{align*}
\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
f & \mapsto \zeta^{-\delta} f
\end{align*}
is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$. This reduces to the previous statement when $\rho = 0$. For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$. Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.

>>>>

If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
\subsection{Main results}
%%\begin{defn}\label{fin-order}
%%Consider a Volterra operator $\mathcal{V}$ of the form
%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
%%\begin{itemize}
%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
%%\end{itemize}
%%and at one of the following holds:
%%\begin{enumerate}
%%\item\label{case:0th-order} $m$ isn't the zero function.
%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
%%\end{enumerate}
%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
%%\end{defn}
The
\begin{thm}

\end{thm}
\begin{thm}
\textcolor{DarkTurquoise}{Existence and uniqueness for deformed operator}
\end{thm}
\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect. It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}. Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
\color{RoyalBlue}
\begin{thm}
Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R}, \]
where
\begin{itemize}
\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item a simple zero at $\zeta = 0$,
\item no zeros in $\Omega$ (as the next condition implies), and
\item a positive lower bound $C_p |z|^d \le |p|$;
\end{itemize}
\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
\begin{itemize}
\item an upper bound $|q| \le C_q |z|^{d-1}$; and
\end{itemize}
\item $\mathcal{R}$ is an integral kernel operator
\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
where $k$ is a holomorphic function on $\Omega^2$, with
\begin{itemize}
\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$.
\end{itemize}
\end{itemize}
Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.

For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
\[ \mathcal{V}f = 0 \]
has a unique solution in the affine subspace
\[ \zeta^{\tau-1} + \holoL{\infty, \tau-1+\epsilon}_\Lambda(\Omega) \]
of the function space $\holoL{\infty, \tau-1}_\Lambda(\Omega)$, defined in Section~\ref{fn-spaces}.
\end{thm}
\color{black}
%%\begin{thm}
%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane. \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}

@@

We now know that by setting $\Lambda > \lambda$ and then increasing $\Lambda$ as needed, we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. This completes our proof of Proposition~\ref{get-contraction}.
%%Let's again integrate along a straight path, where the fact that $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$ allows us to combine the exponential factors in our bound:
%%\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|. \]
%%This time, we'll use the parameterization $\zeta = s \frac{\zeta(a)}{|\zeta(a)|}$, with $s \in (0, |\zeta(a)|]$:
%%\begin{align*}
%%|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{|\zeta(a)|} \left(\frac{s}{|\zeta(a)|}\right)^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
%%\end{align*}
%------------------------------------------------------------------------

\subsection{The test function is in $\singexp{\tau-1}{\lambda}(\Omega)$}

\begin{prop}
    Let $f_0$ be the solution of \textcolor{orange}{Volterra simplified equation}, namely

\begin{equation}\label{eqn:test_solution}
    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]
\end{equation}
for a point $\zeta(b)\in\Omega$. Then $f_0\in\singexp{\tau-1}{\lambda}(\Omega)$. 
\end{prop}

\begin{proof}
    We study separately the case when $\zeta(a)$ is close to the origin and far from the origin.  
\begin{itemize}
    \item \textbf{$\zeta(a)$ close to the origin.} We choose $\varepsilon>0$, then by assumption \eqref{h1} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
  \begin{equation}\label{eqn:limit_h1}
      \Big\vert\frac{q(a')}{p(a)}+\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
  \end{equation}
  notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
  \begin{align*}
      \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{p}{q}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
      &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q(a')+q'(a')(\zeta-\zeta(a')+...)}{p(a')+p'(a')(\zeta-\zeta(a'))+\tfrac{p''(a')}{2}\zeta^2+...}\Big\vert \, |d\zeta|\\
      &\leq \int_{\zeta(b)}^{\zeta(a)} \left\vert\frac{q(a')}{p'(0)\zeta}\right\vert \Big\vert \frac{1+q_1(\zeta-\zeta(a'))+q_2(\zeta-\zeta(a'))^2+...}{1+p_1\zeta+p_2\zeta^2+...}\Big\vert \, |d\zeta|\\
      &\leq c \left\vert\frac{q(a')}{p'(0)}\right\vert \int_{\zeta(b)}^{\zeta(a)} \frac{|d\zeta|}{|\zeta|}  + c \left\vert\frac{q(a')}{p'(0)}\right\vert \int_{\zeta(b)}^{\zeta(a)}\Big\vert \frac{q_1(\zeta-\zeta(a'))+q_2(\zeta-\zeta(a'))^2+...}{\zeta}\Big\vert \, |d\zeta|\\
      &\leq c \left\vert\frac{q(a')}{p'(0)}\right\vert \log\Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert+ C(\delta) 
  \end{align*}
  where in the last step we use that holomorphic function $\frac{q_1(\zeta-\zeta(a'))+q_2(\zeta-\zeta(a'))^2+...)}{\zeta}$ is bounded on $[\tfrac{\delta}{2},\delta]$ and $c>0$. 
  Now we look at $f_0$: let $b'$ such that $|\zeta(b')|\leq \delta$ and $q(b')\neq 0$
  \begin{align*}
      \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]\right\vert &\leq \Big\vert\frac{p(b)}{q(b')}\Big\vert \Big\vert\zeta(a)\frac{q(b')}{p(a)}\Big\vert \Big\vert \zeta(a)\Big\vert^{-1} \exp\left[\left\vert\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta \right\vert\right]\\
      &\leq C_1(\delta) \Big\vert \zeta(a)\Big\vert^{-1} \exp\left[ c \left\vert\frac{q(a')}{p'(0)}\right\vert \log\Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert+ C\right]\\
      &\leq C_1(\delta) \Big\vert \zeta(a)\Big\vert^{-1} \Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau'} \, e^{C(\delta)} \\
      &\leq C_2 |\zeta(a)|^{\tau'-1}
  \end{align*}
  where $\tau':=c \left\vert\frac{q(a')}{p'(0)}\right\vert$. In particular,

  \begin{align*}
      \tau' &\leq \left\vert c\frac{q(a')}{p'(0)}-\zeta(a)\frac{c q(a')}{p(a)}\right\vert + \left\vert\zeta(a)\frac{c q(a')}{p(a)}-\tau\right\vert + \tau\\
      &\leq c |q(a')|\, \left\vert\frac{1}{p'(0)}-\frac{\zeta(a)}{p(a)}\right\vert+\varepsilon+ \tau\\
      &= \frac{c}{|p'(0)|} \frac{|q(a') \zeta(a)|}{|p(a)|} \Big\vert \frac{p(a)}{\zeta(a)}-p'(0)\Big\vert +\tau+\varepsilon\\
      &\leq c_1(\delta,\varepsilon) +  \tau
  \end{align*}
where in the last step we use that $p'(0):=\lim_{\zeta(a)\to 0} \frac{p(a)}{\zeta(a)}$ and $p(0)=0$. 
Finally, we get  
  \begin{align*}
      |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|&\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau'-1} \\&
      \leq C_2(\delta) |\zeta(a)|^{\tau'-\tau} \\
      &\leq C_3(\delta)
  \end{align*}
      \item \textbf{$\zeta(a)$ far to the origin.}
\end{itemize}

\end{proof}

\color{SteelBlue}
\section{Integro-differential equations {[from {\tt airy-resurgence}]}}
\textcolor{DarkTurquoise}{\textbf{Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}}
\subsection{Existence of solutions}
\subsubsection{Algebraic integral operators}
Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$. Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$. For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$. We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
\begin{align*}
\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
\phi & \mapsto \zeta^{-\sigma} \phi
\end{align*}
is an isometry. More generally,
\begin{align*}
\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
f & \mapsto \zeta^{-\delta} f
\end{align*}
is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$. This reduces to the previous statement when $\rho = 0$. For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$. Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.
